---
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    toc_float: yes
---
           

# diffbind - differential peaks           


```{r message=FALSE, warning=FALSE}
library(DiffBind)
library(tidyverse)
library(dplyr)
library(ChIPseeker)
library(TxDb.Mmusculus.UCSC.mm10.knownGene)
library(org.Mm.eg.db)
library(ggplot2)
library(ggpubr)
```

```{r}
## define a function for quick volcano

volpp <- function(res_diffbind, Font=12, volcanoy="p.value", Cnt="ILC2 ATAC KOvsWT", color=c("#CC0000","#BBBBBB","#2f5688")){
  res_diffbind <- data.frame(res_diffbind)
  res_diffbind$Group[res_diffbind$Fold>0] <- "up-regulated"
  res_diffbind$Group[res_diffbind$Fold<0] <- "dn-regulated"
  res_diffbind$Group[res_diffbind[,volcanoy]>0.05] <- "not-significant"
  res_diffbind$Group <- factor(res_diffbind$Group, 
                               levels = c("dn-regulated","not-significant","up-regulated"))
  res_diffbind$logP <- -log10(res_diffbind$p.value)

  maxX <- max(abs(range(res_diffbind$Fold)))*1.1

volplot1 <- ggscatter(res_diffbind, x = "Fold", y = "logP", color = "Group",
                       palette = color,size = 1.5,
                       #label = "Genes",
                       font.label = Font, repel = F,
                       xlab = "diffbind Fold", ylab=paste0("-log10(",volcanoy,")")) + theme_classic() +
    #geom_text_repel(mapping = aes(x = Ret$log2FoldChange, y = Ret$pp, label = Ret$Genes), max.overlaps = 50) +
    guides(color=guide_legend(reverse=TRUE,title = Cnt)) +
    #geom_vline(xintercept = c(-log2(FC),log2(FC)), linetype="dashed") +
    geom_hline(yintercept = -log10(0.05), linetype="dashed") 
volplot1

}

```


## load bam and peaks        

```{r}
samples <- read.csv("samplesheet.cuttag_Rxrg_macs3_q0.25.csv")
samples <- samples[c(4,5,1,2),]
dbObj <- dba(sampleSheet = samples)
```


```{r paged.print=FALSE}
samples
```

```{r paged.print=FALSE}    
dbObj
```


```{r}
# Affinity bind matrix
dbObj <- dba.count(dbObj, bUseSummarizeOverlaps = TRUE, bParallel = TRUE)
```

### FRiP            

```{r paged.print=FALSE}    
dbObj
```

```{r eval=FALSE, include=FALSE}
# 20220410mod
sink(file = "20220410mod/final_cuttag_Rxrg.diff_peak.FRiP.csv",append = F, split = TRUE)
```

```{r}
dbObj
```

```{r eval=FALSE, include=FALSE}
sink()
```


### clustering           

```{r fig.height=5, fig.width=5.6}
dba.plotPCA(dbObj, label = NULL, dotSize = 3.2)
```

```{r eval=FALSE, include=FALSE}
pdf("20220410mod/final_cuttag_Rxrg.diff_peak.PCA.pdf",
    width = 5.6, height = 5)
dba.plotPCA(dbObj, label = NULL, dotSize = 3.2)
dev.off()
```




```{r fig.width=5.1, fig.height=4.8}
plot(dbObj)
```

```{r eval=FALSE, include=FALSE}
pdf("20220410mod/final_cuttag_Rxrg.diff_peak.correlation.pdf",
    width = 5.1, height = 4.8)
plot(dbObj)
dev.off()
```


## run DESeq2/edgeR         


```{r}
dbObj <- dba.contrast(dbObj, categories = DBA_CONDITION, minMembers = 2,contrast = c("Condition","Rxrg_WT","Rxrg_KO"))
```


```{r paged.print=FALSE}
dbObj
```

```{r}
# Performing the differential enrichment analysis
dbObj <- dba.analyze(dbObj, method = DBA_ALL_METHODS)
```

### result             

```{r paged.print=FALSE}
dbObj
```

#### extract all                       

```{r}
res_deseq <- dba.report(dbObj, method = DBA_DESEQ2, contrast = 1, th= 1)
res_edgeR <- dba.report(dbObj, method = DBA_EDGER, contrast = 1, th= 1)
```


### check DESeq2                             

#### top20              

```{r paged.print=FALSE}
data.frame(res_deseq[1:20,])
```

#### one zero       

```{r paged.print=FALSE}
data.frame(res_deseq) %>% filter(Conc_Rxrg_KO ==0 | Conc_Rxrg_WT ==0)
```


#### number             

```{r}
dim(data.frame(res_deseq) %>% filter(p.value < 0.05))
dim(data.frame(res_deseq) %>% filter(p.value < 0.05 & Fold >0))
dim(data.frame(res_deseq) %>% filter(p.value < 0.05 & Fold <0))
```


#### volcano            

```{r}

volpp <- function(res_diffbind, Font=12, volcanoy="p.value", Cnt="ILC2 ATAC KOvsWT", color=c("#CC0000","#BBBBBB","#2f5688")){
  res_diffbind <- data.frame(res_diffbind)
  res_diffbind$Group[res_diffbind$Fold>0] <- "up-regulated"
  res_diffbind$Group[res_diffbind$Fold<0] <- "dn-regulated"
  res_diffbind$Group[res_diffbind[,volcanoy]>0.05] <- "not-significant"
  res_diffbind$Group <- factor(res_diffbind$Group, 
                               levels = c("dn-regulated","not-significant","up-regulated"))
  res_diffbind$logP <- -log10(res_diffbind$p.value)

  maxX <- max(abs(range(res_diffbind$Fold)))*1.1

volplot1 <- ggscatter(res_diffbind, x = "Fold", y = "logP", fill = "Group", 
                       color = "Group",
                       #palette = color,
                       size = 3.5,alpha=0.75, shape = 21,
                       #label = "Genes",
                       font.label = Font, repel = F,
                       xlab = "diffbind Fold", ylab=paste0("-log10(",volcanoy,")")) + theme_classic() +
    #geom_text_repel(mapping = aes(x = Ret$log2FoldChange, y = Ret$pp, label = Ret$Genes), max.overlaps = 50) +
    guides(color=guide_legend(reverse=TRUE,title = Cnt)) +
    #geom_vline(xintercept = c(-log2(FC),log2(FC)), linetype="dashed") +
    geom_hline(yintercept = -log10(0.05), linetype="dashed") 
volplot1

}

```


```{r fig.width=6, fig.height=4.5}
volpp(res_deseq, Font=12, volcanoy="p.value", Cnt="ILC2 CUTTag Rxrg WTvsKO",
      #color = c("#CC0000","#BBBBBB","#2f5688")[2:3]) + 
      color = c("#BBBBBB","black")) + 
  scale_colour_manual(values = c("#6E6E6E","black"))+guides(colour = "none") +
  scale_fill_manual(values = c("#BBBBBB","#F87E79")) +
  labs(title=paste0("DESeq2 differential peaks",
                    "\nup: ",dim(data.frame(res_deseq) %>% filter(p.value < 0.05 & Fold >0))[1],
                    "\ndn: ",dim(data.frame(res_deseq) %>% filter(p.value < 0.05 & Fold <0))[1])) + xlim(c(-1,4.5)) +
  guides(fill = guide_legend(reverse=TRUE))
```

```{r eval=FALSE, include=FALSE}
ggsave("20220410mod/final_cuttag_Rxrg.diff_peak.volcano.pdf",
       plot = last_plot(),
       width = 6, height = 4.5)
```


##### 20220410mod              
edgeR got much more but also higher false-positive ratio ?        
just use DESeq2 results          

```{r}
dim(data.frame(res_edgeR) %>% filter(p.value < 0.05))
```


## 0507mod           

DESeq2 p0.05, plot peak annotation                        


### annotation                


```{r}
peakAnno_deseq <- annotatePeak(res_deseq, tssRegion = c(-3000,3000), TxDb = TxDb.Mmusculus.UCSC.mm10.knownGene,
                                          annoDb="org.Mm.eg.db")
```

#### stat: all          

```{r paged.print=FALSE}
peakAnno_deseq
```


#### stat: p<0.05

```{r paged.print=FALSE}
stat.p0.05 <- data.frame(table(sapply((data.frame(peakAnno_deseq@anno) %>% filter( p.value < 0.05 ))$annotation,
                          function(x) strsplit(x,' (E', fixed = T)[[1]][1] )  ))
stat.p0.05
```


#### stat: p<0.01

```{r paged.print=FALSE}
stat.p0.01 <- data.frame(table(sapply((data.frame(peakAnno_deseq@anno) %>% filter( p.value < 0.01 ))$annotation,
                          function(x) strsplit(x,' (E', fixed = T)[[1]][1] )  ))
stat.p0.01
```


```{r}
res_deseq.p0.05 <- dba.report(dbObj, method = DBA_DESEQ2, contrast = 1, th= 0.05, bUsePval = TRUE)
peakAnno_deseq.p0.05 <- annotatePeak(res_deseq.p0.05, tssRegion = c(-3000,3000), TxDb = TxDb.Mmusculus.UCSC.mm10.knownGene,
                                          annoDb="org.Mm.eg.db")
```

```{r paged.print=FALSE}
peakAnno_deseq.p0.05
```

```{r  fig.height=3.5, fig.width=6, message=FALSE, warning=FALSE}
ChIPseeker::plotAnnoPie(peakAnno_deseq, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E4E290","#E2E2E2"))
```

```{r  fig.height=3.5, fig.width=6, message=FALSE, warning=FALSE}
ChIPseeker::plotAnnoPie(peakAnno_deseq.p0.05, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E5E5E5","#E2E2E2"))
```
```{r}
ChIPseeker::plotAnnoPie.csAnno(peakAnno_deseq.p0.05, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E5E5E5","#E2E2E2"))
```

```{r fig.width=8, fig.height=5}
upsetplot(peakAnno_deseq.p0.05, vennpie=TRUE)
```


```{r eval=FALSE, include=FALSE}
pdf("I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_all.pdf",
    width = 6.5, height = 3.5)
ChIPseeker::plotAnnoPie(peakAnno_deseq, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E4E290","#E2E2E2"))

dev.off()

pdf("I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_p0.05.pdf",
    width = 6.5, height = 3.5)
ChIPseeker::plotAnnoPie.csAnno(peakAnno_deseq.p0.05, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E5E5E5","#E2E2E2"))
dev.off()
```


#### 0525mod         

```{r fig.height=3.5, fig.width=6}
ChIPseeker::plotAnnoPie(peakAnno_deseq, cex = 0.25,ndigit = 2,
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E4E290","#E2E2E2"),
                        lty=1,lwd=0.001,border=NA)
```

```{r  fig.height=3.5, fig.width=6, message=FALSE, warning=FALSE}
ChIPseeker::plotAnnoPie(peakAnno_deseq.p0.05, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E5E5E5","#E2E2E2"),
                        lty=1,lwd=0.001,border=NA)
```


```{r eval=FALSE, include=FALSE}
pdf("I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_all.thin0525.pdf",
    width = 6.5, height = 3.5)
ChIPseeker::plotAnnoPie(peakAnno_deseq, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E4E290","#E2E2E2"),
                        lty=1,lwd=0.1,border=NA)

dev.off()

pdf("I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_p0.05.thin0525.pdf",
    width = 6.5, height = 3.5)
ChIPseeker::plotAnnoPie.csAnno(peakAnno_deseq.p0.05, 
                               col = c("#A1CBDB","#47A3B9","#057DC4","#6E9F4E","#F16B61",
                                       "#F46F40","#F5902E","#DABC86","#BDBEC0","#E5E5E5","#E2E2E2"),
                        lty=1,lwd=0.1,border=NA)
dev.off()
```


#### top annotation           

```{r paged.print=FALSE}
#data.frame(peakAnno_deseq@anno)[1:100,c(1:11,12,20,22,23)][1:50,]
```



#### save annotated csv              

```{r eval=FALSE, include=FALSE}
write.table(data.frame(peakAnno_deseq@anno) %>% arrange(p.value), 
            "I:/Shared_win/projects/202204_RxrgILC2/peak_anno/ILC2_CUTTag_Rxrg.macs3_q0.25.diffbind_deseq2.anno_all.tsv",
            col.names = T, row.names = F, sep = "\t", quote = F)

#write.csv(print(peakAnno_deseq),
#          "I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_all.tsv")


#
write.table(data.frame(peakAnno_deseq.p0.05@anno) %>% arrange(p.value), 
            "I:/Shared_win/projects/202204_RxrgILC2/peak_anno/ILC2_CUTTag_Rxrg.macs3_q0.25.diffbind_deseq2.anno_p0.05.tsv",
            col.names = T, row.names = F, sep = "\t", quote = F)




```




```{r eval=FALSE, include=FALSE}
# 20220507mod
sink(file = "I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_all.tsv",append = F, split = TRUE)
```

```{r paged.print=FALSE}
peakAnno_deseq
```

```{r eval=FALSE, include=FALSE}
sink()
```


```{r eval=FALSE, include=FALSE}
# 20220507mod
sink(file = "I:/Shared_win/projects/202204_RxrgILC2/peak_anno/stat.anno_p0.05.tsv",append = F, split = TRUE)
```

```{r paged.print=FALSE}
peakAnno_deseq.p0.05
```

```{r eval=FALSE, include=FALSE}
sink()
```


